---
title: "Tree Application"
author: "Mikhail Chernykh"
date: "Monday, February 23, 2015"
output: slidy_presentation
---

## Tree Application is fun!
```{r, echo=FALSE}
set.seed(1)
rotMatrix <- function(angle) {
      matrix(c(cos(angle), sin(angle), -sin(angle), cos(angle)), 2, 2)
    }
drawLines <- function (depth, root, direction) {
  colors <- colorRamp(c("#05B311", "#F2BE2E"))
  if (!depth %in% 1:15) {
    return()
  }
  ang <- input$angle
  lwd <- ifelse(input$clwd, input$lwd, depth + 1)
  color <- rgb(colors(depth / as.numeric(input$depth)) / 255)
  lines(c(root[1], root[1] + direction[1]), c(root[2], root[2] + direction[2]), lwd = lwd, col = color)
  
  new_root <- root + direction / 2
  direction <- direction * 2 / 3
  
  new_direction_one <- rotMatrix(ang) %*% direction
  new_direction_two <- rotMatrix(-ang) %*% direction
  new_depth <- depth - 1
  drawLines(new_depth, new_root, new_direction_one)
  drawLines(new_depth, new_root, new_direction_two)
}

plotRandomTree <- function() {
  input <- list(angle = runif(1, min = 0.05, max = 1), depth = sample(2:12, 1), clwd = runif(1) > 0.5, lwd = sample(1:5, 1))
  plot(0:10, 0:10, type = "n", main = "Here is your tree!")
  drawLines(as.numeric(input$depth), c(5, 0), c(0, 7))
}
```

```{r, echo=FALSE,results='hide'}
input <- list(angle = 0.3, depth = 13, clwd = FALSE, lwd = 2)
plot(0:10, 0:10, type = "n", main = "Here is your tree!")
drawLines(as.numeric(input$depth), c(5, 0), c(0, 7))

```

---

## Customize your tree!

- Select "depth" (actually, it grows up) of your tree by selector  

- Choose angle between tree leaves, wide range of opportunities. Do you want to turn your tree upside... to inside? No problem!

- Customize width of your tree, make it constant of make it automatically calculated!

- Set exact value for width of lines used to draw a tree if you wish. (Values above 5 will be available in Pro+ version of tree app, stay tuned!)

---

## Variety of trees is astonishing!
```{r}
par(mfrow = c(2,4))
for(i in 1:8) {
  invisible(plotRandomTree())  
}
```

---

## Thanks for attention!

Feel free to preorder Tree App Pro+, even more customizable and amazing!
